---
title: "Wikipedia Caption Analysis"
output: rmarkdown::github_document  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(cowplot)
library(tidyverse)

theme_set(theme_cowplot())
theme_set(theme_bw(18))
```


# Wikipedia distribution

```{r}

wiki_sample = read_csv("../ratio_estimates.csv")

# wiki_sample = tibble(
#   sample = c(1,2,3,4,5,6,7,8),
#   num_lines = c(226795,1230026,5267645,10157289,10658404,11119761,15252703,20072825),
#   images = c(7427,6166,9862,6246,4311,4758,755,1751),
#   descriptions = c(663,321,842,347,226,234,15,138),
#   captions = c(6368,5413,8604,4751,3605,3728,680,1481)
# )

wiki_sample

wiki_data = wiki_sample %>% 
  filter(images > 0) %>% 
  mutate(descr_prop = descriptions/images,
         caption_prop = captions/images) %>% 
  select(images, descr_prop, caption_prop) %>% 
  gather(text_type, value, descr_prop, caption_prop) %>% 
  mutate_at(vars(text_type), funs(case_when(
    . == "caption_prop" ~ "Proportion of\ncaptions",
    . == "descr_prop" ~ "Proportion of\ndescriptions",
    TRUE ~ "other")))

glimpse(wiki_data)

wiki_data %>% 
  ggplot(., aes(x=text_type, y=value, color=text_type)) +
    facet_grid(~text_type, scales = "free") +
    ylim(0,1) +
    # geom_point(alpha = 0.3,
    #            size = 4,
    #            color = "black",
    #            position = position_jitter(height=0, width = 0.02)) +
    geom_violin(color="black", fill="black", alpha=0.1) +
    stat_summary(fun = mean,
                 geom = "point",
                 size = 5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 size = .5,
                 width = 0.1) +
    scale_color_manual(values=c('#fc8d62', '#66c2a5')) +
    theme(legend.position = "none") +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())

# wiki_data = wiki_sample %>% 
#   mutate(img_per_article = images/1000,
#          prop_img_w_descr = descriptions/images,
#          prop_img_w_caption = captions/images) %>% 
#   select(sample, prop_img_w_descr, prop_img_w_caption, img_per_article) %>% 
#   gather(metric, value, prop_img_w_caption, prop_img_w_descr, img_per_article) %>% 
#   mutate_at(vars(metric), funs(case_when(
#     . == "prop_img_w_caption" ~ "Proportion of\ncaptions", 
#     . == "prop_img_w_descr" ~ "Proportion of\ndescriptions",
#     TRUE ~ "Number of\nimages per article")))
# 
# wiki_data %>% 
#   filter(metric != "Number of\nimages per article") %>% 
#   ggplot(., aes(x=metric, y=value, color=metric)) +
#     facet_grid(~metric, scales = "free") +
#     ylim(0,1) +
#     geom_point(alpha = 0.3, 
#                size = 4, 
#                color = "black", 
#                position = position_jitter(height=0, width = 0.02)) +
#     stat_summary(fun = mean,
#                  geom = "point",
#                  size = 5) +
#     stat_summary(fun.data = "mean_cl_boot",
#                  geom = "errorbar",
#                  size = .5,
#                  width = 0.1) +
#     scale_color_manual(values=c('#fc8d62', '#66c2a5')) +
#     theme(legend.position = "none") +
#     theme(axis.title = element_blank(),
#           axis.text.x = element_blank(),
#           axis.ticks.x = element_blank())
# 
# wiki_data %>% 
#   filter(metric == "Number of\nimages per article") %>% 
#   ggplot(., aes(x=metric, y=value, color=metric)) +
#     facet_grid(~metric, scales = "free") +
#     # ylim(0,1) +
#     geom_point(alpha = 0.3, 
#                size = 4, 
#                color = "black", 
#                position = position_jitter(height=0, width = 0.02)) +
#     stat_summary(fun = mean,
#                  geom = "point",
#                  size = 5) +
#     stat_summary(fun.data = "mean_cl_boot",
#                  geom = "errorbar",
#                  size = .5,
#                  width = 0.1) +
#     scale_color_manual(values=c('blue')) +
#     theme(legend.position = "none") +
#     theme(axis.title = element_blank(),
#           axis.text.x = element_blank(),
#           axis.ticks.x = element_blank())
# 
mean(wiki_data[wiki_data$text_type=="Proportion of\ncaptions",]$value)
mean(wiki_data[wiki_data$text_type=="Proportion of\ndescriptions",]$value)

# ggsave("wiki_sample.png", height=3.5,width=6)

```



```{r data import, include=FALSE}
df = read_csv("final_data.csv") %>% 
  rename(description_raw = description,
         caption_raw = caption,
         file_raw = filename)
```

```{r clean df, include=FALSE}

df_clean = df %>% 
  mutate(description = str_replace(description_raw, "\\{'raw': ['\\\"]", "")) %>% 
  mutate_at(vars(description), funs(str_replace(., "['\\\"], 'tokens': \\[.*", ""))) %>% 
  mutate(caption = str_replace(caption_raw, "\\{'raw': ['\\\"]", "")) %>% 
  mutate_at(vars(caption), funs(str_replace(., "['\\\"], 'tokens': \\[.*", "")))

# 41143
length(unique(df_clean$article_id))

# 96918
nrow(df_clean)

df_clean %>% 
  group_by(split) %>% 
  summarize(data = n()) %>% 
  ungroup

df_clean %>% 
  distinct(article_id, split) %>% 
  group_by(split) %>% 
  summarize(data = n()) %>% 
  ungroup

df_clean %>%
  rowid_to_column("ID") %>% 
  gather(type, text, description, caption) %>% 
  # group_by(split, type) %>%
  group_by(type) %>%
  mutate(characters = str_length(text)) %>% 
  mutate(words = str_count(text, boundary("word"))) %>% 
  summarize(avg_nr_of_words = mean(words),
            avg_nr_of_chars = mean(characters)) %>% 
  ungroup() %>% 
  mutate(avg_word_len = avg_nr_of_chars/avg_nr_of_words)

```

# Length difference

Descriptions are longer but captions have longer words.

```{r length, echo=FALSE, fig.asp=0.6}
df_main = df_clean %>%
  rowid_to_column("ID") %>% 
  gather(type, text, description, caption) %>% 
  mutate(characters = str_length(text)) %>% 
  mutate(words = str_count(text, boundary("word")))

df_main %>% 
  gather(len_param, length, characters, words) %>% 
  ggplot(., aes(x=type, y=length, fill=type)) + 
    facet_wrap(~len_param, scales = "free_y") + 
    stat_summary(fun = mean,
                 geom = "bar",
                 color = "black",
                 position = position_dodge(0.9)) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 size = .3,
                 width = 0.3,
                 position = position_dodge(0.9)) +
    theme(legend.position = "none") +
    scale_fill_manual(values=c('#fc8d62', '#66c2a5')) +
    theme(strip.background = element_rect(fill="white")) +
    xlab("") +
    ylab("Average length")

# ggsave("caption_descr_length.png", height=3.5,width=6)

df_main %>% 
  gather(len_param, length, characters, words) %>% 
  mutate(cond = str_c(type, len_param, sep="_")) %>% 
  ggplot(., aes(x=type, y=length, fill=cond)) + 
    # facet_wrap(~len_param, scales = "free_y") + 
    stat_summary(fun = mean,
                 geom = "bar",
                 color = "black",
                 position = position_dodge(0.9)) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 size = .3,
                 width = 0.3,
                 position = position_dodge(0.9)) +
    theme(legend.position = "none") +
    scale_fill_manual(values=c('#fca381', '#c9704e', '#84ceb7', '#519b84')) +
    theme(strip.background = element_rect(fill="white")) +
    xlab("") +
    ylab("Average length")

```

There is no correlation of description and caption length (here, measure in number of words), i.e., it's not the case that images that receive long captions, also receive long descriptions and vice versa.

```{r length correlation, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_plot = df_clean %>%  
  mutate(descr_word_len = str_count(description, boundary("word"))) %>% 
  mutate(caption_word_len = str_count(caption, boundary("word")))

ggplot(df_plot, aes(x=descr_word_len, y=caption_word_len)) +
  geom_abline(color = "gray40", lty = 2) +
  geom_point(alpha=0.2, color="#526f8b") +
  theme(legend.position = "none") +
  xlim(0,200) +
  ylim(0,200) +
  xlab("Description length") +
  ylab("Caption length")
  # geom_smooth(method="lm")


```

# Similarity between captions and corresponding descriptions

```{r similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.asp=0.8, fig.width=5, out.width="50%"}
library(hashr)
library(stringdist)

calc_jacc_dist = function(string_1,string_2){
  # convert strings to list of unique words 
  # case doesn't matter:
  list_1 = strsplit(str_to_lower(string_1),split = " ")[[1]]
  list_2 = strsplit(str_to_lower(string_2),split = " ")[[1]]
  # compare lists according to cardinality of intersection / cardinality of union
  inters_cardinality = length(intersect(list_1,list_2))
  union_cardinality = length(union(list_1,list_2))
  dist = 1 - (inters_cardinality/union_cardinality)
  dist
}

df_dist = df_clean %>% 
  # head(.,n=10000) %>% 
  rowwise() %>% 
  mutate(dist = calc_jacc_dist(description, caption)) %>% 
  ungroup() %>% 
  mutate(caption_shuffled = sample(caption, replace=FALSE)) %>% 
  rowwise() %>% 
  mutate(dist_shuffled = calc_jacc_dist(description, caption_shuffled))

df_dist %>% 
  select(dist, dist_shuffled) %>% 
  gather(condition, value) %>%  
  ggplot(., aes(x=value, color=condition, fill=condition)) +
    geom_histogram(binwidth=0.05, color="#e9ecef", alpha=0.5, position = 'identity') +
    theme(legend.position = "top") +
    xlab("Distance") +
    ylab("Number of instances") +
    scale_fill_manual(name = "",
                       labels = c("dist" = "Original", 
                                  "dist_shuffled" = "Shuffled"),
                       values=c("#d7191c", "#abd9e9"))

df_dist %>% 
  select(dist, dist_shuffled) %>% 
  gather(condition, value) %>% 
  mutate_at(vars(condition), funs(ifelse(.=="dist", "Original", "Shuffled"))) %>% 
  ggplot(., aes(x=condition, y=value, color=condition, fill=condition)) +
    geom_violin(color="black", fill="black", alpha=0.2) +
    stat_summary(fun = mean,
                 geom = "point",
                 size = 5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 size = .3,
                 width = 0.1) +
    theme(legend.position = "none") +
    scale_color_manual(values=c("#d7191c", "#2c7bb6")) +
    coord_cartesian(ylim=c(0,1)) +
    ylab("Distance") +
    xlab("")

# ggsave("jacc_distance.png", height=3.5,width=5)

mean(df_dist$dist)

ks.test(df_dist$dist, df_dist$dist_shuffled)

```

```{r}
sbert_cosine_sim = read_csv("sbert_sim.csv") %>% 
  select(-X1) %>% 
  gather(condition, value) %>% 
  mutate_at(vars(condition), funs(ifelse(.=="match_sim", "Original", "Shuffled")))

sbert_cosine_sim %>% 
  ggplot(., aes(x=condition, y=value, color=condition, fill=condition)) +
    geom_violin(color="black", fill="black", alpha=0.2) +
    stat_summary(fun = mean,
                 geom = "point",
                 size = 5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 size = .3,
                 width = 0.1) +
    theme(legend.position = "none") +
    scale_color_manual(values=c("#d7191c", "#2c7bb6")) +
    coord_cartesian(ylim=c(0,1)) +
    ylab("Similarity") +
    xlab("")

nrow(sbert_cosine_sim)/2

# ggsave("sbert-sim.png", height=3.5,width=5.5)

sbert_cosine_sim %>% 
  group_by(condition) %>% 
  summarise(avg = mean(value))

ks.test(sbert_cosine_sim[sbert_cosine_sim$condition=="Original",]$value,
        sbert_cosine_sim[sbert_cosine_sim$condition=="Shuffled",]$value)

```


```{r pos analysis}

descr_pos = read_csv("pos_tags_descr.csv") %>% 
  rename(tags="descr_tags")

sum_descr_pos = descr_pos %>% 
  group_by(tags) %>% 
  summarize(descr_frq = n()) %>% 
  ungroup()

caption_pos = read_csv("pos_tags_caption.csv") %>% 
  rename(tags="caption_tags")

sum_caption_pos = caption_pos %>% 
  group_by(tags) %>% 
  summarize(caption_frq = n()) %>% 
  ungroup()

all_pos = sum_descr_pos %>% 
  left_join(sum_caption_pos) %>% 
  gather(text, frq, descr_frq, caption_frq) %>% 
  group_by(text) %>% 
  mutate(prop_frq = frq/sum(frq)) %>% 
  ungroup()

all_pos %>% 
  mutate_at(vars(text), funs(ifelse(.=="caption_frq", "captions", "descriptions"))) %>%
  ggplot(., aes(x=reorder(tags,-prop_frq), y=prop_frq, fill=text)) +
    geom_bar(stat="identity",
             width=0.8,
             position = position_dodge(0.8)) +
    theme(axis.text.x = element_text(angle = 30,hjust=1)) +
    scale_fill_manual(values=c('#fc8d62', '#66c2a5')) +
    theme(legend.position = "top") +
    ylab("Proportion of POS tags") +
    xlab("POS tags")

# ggsave("postags.png", height=5,width=14)
 
bind_rows("description" = descr_pos, "caption" = caption_pos, .id="condition") %>%
  mutate(PN = ifelse(tags=="NNP" | tags=="NNPS", 1, 0)) %>% 
  ggplot(., aes(x=condition, y=PN, fill=condition)) +
    stat_summary(fun = mean,
                 geom = "bar",
                 color = "black",
                 width = 0.5,
                 position = position_dodge(0.8)) +
    # takes a long time to compute and standard error is around 0
    # stat_summary(fun.data = "mean_cl_boot",
    #              geom = "errorbar",
    #              size = .3,
    #              width = 0.2,
    #              position = position_dodge(0.8)) +
    scale_fill_manual(values=c('#fc8d62', '#66c2a5')) +
    theme(legend.position = "none",
          axis.title.x = element_blank()) +
    ylab("Proportion of proper nouns")

df_interpr_tags = sum_descr_pos %>% 
  left_join(sum_caption_pos) %>% 
  gather(text, frq, descr_frq, caption_frq) %>% 
  mutate_at(vars(text), funs(ifelse(.=="caption_frq", "captions", "descriptions"))) %>%
  mutate(interpr_tags = case_when(
    str_starts(tags,"NNP") ~ "proper nouns",
    tags == "NN" | tags == "NNS" ~ "nouns",
    str_starts(tags, "JJ") ~ "adjectives",
    str_starts(tags,"VB") ~ "verbs",
    str_starts(tags,"PRP") ~ "pronouns",
    TRUE ~ "other"
  )) %>% 
  filter(interpr_tags != "other") %>%
  group_by(interpr_tags, text) %>% 
  summarize(bin_frq = sum(frq)) %>% 
  ungroup() %>% 
  group_by(text) %>% 
  mutate(prop_frq = bin_frq/sum(bin_frq),
         std = sqrt(
           (bin_frq*((1-prop_frq)^2) + 
              (sum(bin_frq)-bin_frq)*((0-prop_frq)^2)) / sum(bin_frq)),
         ci_up = prop_frq + ((1.96 * std)/sqrt(sum(bin_frq))),
         ci_low = prop_frq - ((1.96 * std)/sqrt(sum(bin_frq)))) %>% 
  ungroup()

df_interpr_tags %>% 
  mutate_at(vars(interpr_tags), funs(fct_relevel(.,levels=c("proper nouns", "nouns", "adjectives", "verbs", "pronouns")))) %>% 
  ggplot(., aes(x=interpr_tags, y=prop_frq, fill=text)) +
    geom_bar(stat="identity",
             width=0.8,
             color="black",
             alpha=0.75,
             position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=ci_low,
                      ymax=ci_up), 
                  stat="identity",
                  width=0.3,
                  color="black",
                  position = position_dodge(0.8)) +
    scale_fill_manual(name="",
                      labels=c("caption","description"),
                      values=c('#ee7733','#009988')) +
    theme(legend.position = "top") +
    ylab("Proportion of occurrence") +
    xlab("Part-of-Speech")

ggsave("poscomparison.png", height=4,width=8)

df_interpr_tags

```



# Most frequent words

```{r freq data prep, include=FALSE}
library(tidytext)

df_descr_word = df_clean %>% 
  select(article_id, description) %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words)

df_caption_word = df_clean %>% 
  select(article_id, caption) %>% 
  unnest_tokens(word, caption) %>%
  anti_join(stop_words)

frequency <- bind_rows(mutate(df_descr_word, category = "Description"),
                       mutate(df_caption_word, category = "Caption")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(category, word) %>%
  group_by(category) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  arrange(-proportion)
  # spread(category, proportion)

```

Captions require a bigger vocabulary/lexicon (12% of all word occurrences are unique) than descriptions (8% of all word occurrences are unique).

```{r unique words, include=FALSE}

df_descr_word = df_clean %>% 
  filter(split == "test") %>% 
  select(article_id, description) %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words)

df_caption_word = df_clean %>% 
  filter(split == "test") %>% 
  select(article_id, caption) %>% 
  unnest_tokens(word, caption) %>%
  anti_join(stop_words)

nrow(df_descr_word)
length(unique(df_descr_word$word))
# Descriptions -- Proportion of unique words: 8%
length(unique(df_descr_word$word))/nrow(df_descr_word)

nrow(df_caption_word)
length(unique(df_caption_word$word))
# Captions -- Proportion of unique words: 13%
length(unique(df_caption_word$word))/nrow(df_caption_word)


```

Descriptions in green and captions in red. 
"th" and "st" are probably from 24**th** and **st**reet.

```{r word clouds, echo=FALSE, fig.width=9, message=FALSE, warning=FALSE, out.width="100%", paged.print=FALSE}
library(wordcloud)
library(RColorBrewer)

par(mfrow=c(1,2))

pal <- brewer.pal(9, "BuGn")
pal <- pal[-(1:3)]

df_descr_wcount = df_descr_word %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  filter(!is.na(word)) %>% 
  count(word)

df_descr_wcount %>%
  with(wordcloud(word,
                 n,
                 max.words = 100,
                 scale=c(3,.6),
                 colors = pal
                 # vfont=c("sans serif","plain")
                 ))

pal <- brewer.pal(9, "OrRd")
pal <- pal[-(1:3)]

df_caption_wcount = df_caption_word %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  filter(!is.na(word)) %>% 
  count(word) %>% 
  arrange(-n)

df_caption_wcount %>%
  with(wordcloud(word, 
                 n, 
                 max.words = 100, 
                 scale=c(2.1,.4),
                 colors = pal
                 # vfont=c("sans serif","plain")
                 ))
```


### Description

Meta-information, e.g., *photograph*, *photo*, and probably *black* and *white* from *black and white photograph*.
Colors in general (*white, black, red, blue*), location (*left, front*) and descriptive primitives (*wearing, map*).

```{r freq descr, echo=FALSE}
df_descr_word %>%
  count(word, sort = TRUE) %>% 
  head(., n=10)

# frequency %>% 
#   filter(!is.na(word)) %>% 
#   filter(word != "ref",
#          word != "nbsp") %>% 
#   filter(category=="Description") %>% 
#   arrange(-proportion)
  

```

### Caption

Less primitive descriptives (like colors) and more extra-image information (*won, century, john, view, 2009*).

```{r freq caption, echo=FALSE}
df_caption_word %>%
  count(word, sort = TRUE) %>% 
  head(., n=10)

# frequency %>% 
#   filter(!is.na(word)) %>% 
#   filter(word != "ref",
#          word != "nbsp") %>% 
#   filter(category=="Caption") %>% 
#   arrange(-proportion)
```

## Word frequency difference

Highly correlated (Pearson: *r=0.52*, *p<0.0001*), but clear patterns. 

```{r freq difference, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

library(scales)

# count = bind_rows(mutate(df_descr_word, category = "Description"),
#                        mutate(df_caption_word, category = "Caption")) %>% 
#   mutate(word = str_extract(word, "[a-z']+")) %>%
#   count(category, word) %>% 
#   arrange(-n)

# frequency %>% 
#   # gather(category, value, Caption, Description) %>% 
#   ggplot(., aes(x=proportion, color=category, fill=category)) +
#     geom_histogram(alpha=0.4) +
#     coord_cartesian(xlim=c(0,0.015), ylim = c(0,30))

df_frq_plot = frequency %>% 
  filter(!is.na(word)) %>% 
  spread(category, proportion)

df_frq_plot %>% 
  ggplot(., aes(x=Description, y=Caption,color=abs(Description - Caption))) +
    geom_abline(color = "gray40", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    # geom_point(alpha = 0.1, size = 2.5) +
    geom_text(aes(label = word), check_overlap = TRUE) +
    scale_color_gradient(limits = c(0, 0.001), low = "#526f8b", high = "gray75") +
    theme(legend.position="none") +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format())

# ggsave("word_frq_corr.png", height=5,width=8)

```

```{r frq corr, include=FALSE}
# Pearson's product-moment correlation
# 0.5243, p<0.0001
cor.test(data = df_frq_plot,
         ~ Description + Caption)
```

# Ngram analysis

### Most frequent trigrams with stopwords

Captions contain proper names (*united states*, *tour de france*), addresses events (*the battle of*) and extra-information (*part of the*, *was the first*, *of the first*).
Descriptions contain a variety of locations (*foreground, background, front, left*), basic category reference to a person (*man*), clothing descriptives (*wearing*) and meta-photo information (multiple variants of *black and white photograph*).

```{r ngram stopw, echo=FALSE, fig.width=10, fig.height=4.5}

# df_descr_bigram = df_clean %>% 
#   select(article, description) %>% 
#   unnest_tokens(word, description, token = "ngrams", n = 2) %>% 
#   count(word) %>% 
#   arrange(-n) %>% 
#   head(n=20)

# df_caption_bigram = df_clean %>% 
#   select(article, caption) %>% 
#   unnest_tokens(word, caption, token = "ngrams", n = 2) %>% 
#   count(word) %>% 
#   arrange(-n) %>% 
#   head(n=20)

df_descr_trigram = df_clean %>% 
  select(article_id, description) %>% 
  unnest_tokens(word, description, token = "ngrams", n = 3) %>% 
  count(word, sort=TRUE) %>% 
  head(n=15) %>% 
  mutate(condition = "description")

df_caption_trigram = df_clean %>% 
  select(article_id, caption) %>% 
  unnest_tokens(word, caption, token = "ngrams", n = 3) %>% 
  count(word, sort=TRUE) %>% 
  head(n=15) %>% 
  mutate(condition = "caption")

df_caption_trigram %>%
  rbind(df_descr_trigram) %>% 
  filter(!is.na(word)) %>% 
  ggplot(., aes(x=reorder_within(word,n,condition), 
                y=n, 
                fill=condition)) +
    facet_wrap(~condition, scales = "free") +
    ylab("") +
    xlab("") +
    scale_x_reordered() +
    geom_bar(stat="identity", 
             width=0.9) +
    coord_flip() +
    scale_fill_manual(values=c('#fc8d62', '#66c2a5')) +
    theme(strip.background = element_rect(fill="white")) +
    theme(legend.position = "none")

# ggsave("trigrams.png", height=4.5,width=10)

```

### Most frequent bigrams without stopwords

Captions are dominated by events and proper names.
Descriptions are dominated by terms relating to appearance.

```{r ngram nostopw, echo=FALSE, fig.width=10, fig.height=4.5}

df_descr_bigram = df_clean %>% 
  select(article_id, description) %>% 
  unnest_tokens(trigram, description, token = "ngrams", n = 2) %>% 
  separate(trigram, c("word1", "word2"), sep = " ") %>%
  filter(
    !word1 %in% stop_words$word,
    !word2 %in% stop_words$word
  ) %>%
  count(word1, word2, sort = TRUE) %>% 
  unite(bigram, word1:word2, remove=TRUE, sep=" ") %>% 
  filter(!str_detect(bigram, "NA NA")) %>% 
  head(n=15) %>% 
  mutate(condition = "description")

df_caption_bigram = df_clean %>% 
  select(article_id, caption) %>% 
  unnest_tokens(trigram, caption, token = "ngrams", n = 2) %>% 
  separate(trigram, c("word1", "word2"), sep = " ") %>%
  filter(
    !word1 %in% stop_words$word,
    !word2 %in% stop_words$word
  ) %>%
  count(word1, word2, sort = TRUE) %>% 
  unite(bigram, word1:word2, remove=TRUE, sep=" ") %>% 
  filter(!str_detect(bigram, "NA NA")) %>% 
  head(n=15) %>% 
  mutate(condition = "caption")

df_caption_bigram %>%
  rbind(df_descr_bigram) %>% 
  ggplot(., aes(x=reorder_within(bigram,n,condition), 
                y=n, 
                fill=condition)) +
    facet_wrap(~condition, scales = "free") +
    ylab("") +
    xlab("") +
    scale_x_reordered() +
    geom_bar(stat="identity", 
             width=0.4,
             # color="darkgrey",
             alpha=0.75) +
    coord_flip() +
    scale_fill_manual(values=c('#ee7733','#009988')) +
    theme(strip.background = element_rect(fill="white")) +
    theme(legend.position = "none",
          strip.text = element_text(size=18))

ggsave("bigrams-nostopw.png", height=4.1,width=9.15)

```

